Practical Machine Learning Project
===

---

### Abstract

This is the project of practical machine learning class in Cousera.
The goal of this project is to predict the manner in which a certain person's exercise.


The training data for this project are available here: 
https://d396qusza40orc.cloudfront.net/predmachlearn/pml-training.csv


The test data are available here: 
https://d396qusza40orc.cloudfront.net/predmachlearn/pml-testing.csv


The variable to predict is "classe" variable in the training data.


---

### Loading Data

At first, I load the training data and testing data.

```{r message=FALSE}
library(data.table)
setwd(dir = "C:/Users/masahiro/Documents/_Practical_Machine_Learning/Project")
training<-fread("pml-training.csv",na.strings=c("NA","#DIV/0!",""))
testing<-fread("pml-testing.csv",na.strings=c("NA","#DIV/0!",""))
```

### Cleaning Data

The raw data is not suitable for machine learning.
So the data should be cleaned before processing.

The columns in testing data which are not available and same variables in training data will be removed.
And factor variables whose class is character will be converted to factor class.

```{r message=FALSE}
### testing data
testing<-testing[,colSums(is.na(testing))<nrow(testing),with=FALSE]
testing<-testing[,V1:=NULL]
testing<-testing[,problem_id:=NULL]
testing<-testing[,cvtd_timestamp:=NULL]
testing$user_name<-as.factor(testing$user_name)
testing$new_window<-as.factor(testing$new_window)

### training data
training<-training[,c(which(names(training)%in%names(testing)),which(names(training)=="classe")),with=FALSE]
training$user_name<-as.factor(training$user_name)
training$new_window<-as.factor(training$new_window)
training$classe<-as.factor(training$classe)
```

---

### Training with Cross Validation

I have selected Random Forest algorithm as training method and repeatedcv as cross varidation method.

```{r message=FALSE}
library(caret)
set.seed(1235)

modelFit<-train(classe~.,data=training,method="rf",trControl=trainControl(method="repeatedcv",number=3,repeats=1))

modelFit
```

---


### Prediction

Finlally, I predict the classe variable for the each test data.

```{r message=FALSE}
predict(modelFit,newdata=testing)
```

---
